---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# palabras

<!-- badges: start -->
[![R-CMD-check](https://github.com/stemterminalgutter/palabras/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/stemterminalgutter/palabras/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of palabras is to be a random word generator. It also can create a 
 wordcloud based off frequently used words. Finally, a word game. For fun. 
 No one will probably use this but myself and my professor. 

## Installation

You can install the development version of palabras like so:

```
$ git clone https://github.com/stemterminalgutter/palabras
```

## Example

See below :

```{r example}
library(palabras)

word_path <- file.path(getwd(), "words_alpha.txt")
huge_word_list <- readLines(word_path)

generate_random_words <- function(n, huge_word_list) {
  sample(huge_word_list, n, replace = TRUE)
}

random_words <- generate_random_words(1, huge_word_list)
print(random_words)

```

What is special about this random word generator? Nothing in particular. But
at least you can play a game if you get bored with life -- also, isn't it 
great to play around with words you've probably never heard of?

```{r}
print(random_words)
```
